Discussion

### 2023-04-06 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
rephrasing

Our goal was to calculate individual subjective values to develop a better understanding of ER stratagem selection.
Most individuals show great variability in the choice of strategies, both, within-strategy and between-strategy[@Blanke2020;@Burr2020;@Elkjaer2022]. 
Greater variability might even adaptive [@Blanke2020;@Aldao2015].
In addition, a wide variety of factors that influence the choice of strategies in specific situations were examined[@Scheffel2021;@Sheppes2011;@Sheppes2014;@Wilms2020;@Young2020;@Matthews2021], including intensity of the situation and effort.
However, these factors have often been studied separately.
Only rarely have effects of the factors been studied in combination[@Young2020].
Moreover, the usual paradigms used in ER choice research (e.g., Sheppes et al.[@Sheppes2011]) can only estimate how a factor tends to drive the choice in one direction or the other.
However, it cannot be determined in this way what internal subjective value individuals attribute to the choice options.
We are confident that we have succeeded in this with the present paradigm.
On the one hand, we were able to show which factors influence the values, but on the other hand, we were able to show the actual practical relevance of the values.
The highest SVs of the individuals were associated with the choice made by the participants. 
Until now, it has been difficult to transfer such findings from the laboratory to everyday life[@Wilms2020].
This may be due to the fact that in laboratory studies, the choice options are often predetermined by the design of the experiment [@Sheppes2011;@Sheppes2014;@Scheffel2021].
It was therefore attempted to investigate ER choice and influencing factors in everyday life.
However, even there, certain strategies were often prescribed (for example studies, see English et al.[@English2017], Millgram et al.[@Millgram2019], Wilms et al.[@Wilms2020]). 
Although these covered a large area of the emotion-genesis process[@Gross1998emerging], they were nevertheless ultimately fixed.
Of course, the calculation of SVs in our new CAD paradigm is tied to the strategies with which the strategy of interest is compared.
However, it would be possible to use ecological momentary assessment to capture ER strategies[@Koval2020].
This would allow all strategies of the ER repertoire to be recorded for each individual[@Aldao2015]. 
Also those that are rarely used or even marked as maladaptive, such as alcohol consumption or rumination[@Pena-Sarrionandia2015].

>>>>

Our aim was to calculate individual subjective values in order to develop a better understanding of ER strategy selection.
Most individuals show large variability in strategy choice, both within-strategy and between-strategy[@Blanke2020;@Burr2020;@Elkjaer2022]. 
Greater variability may even be adaptive[@Blanke2020;@Aldao2015].
In addition, a variety of factors that influence strategy choice in specific situations have been examined[@Scheffel2021;@Sheppes2011;@Sheppes2014;@Wilms2020;@Young2020;@Matthews2021], including situation intensity and effort.
However, these factors have often been studied separately.
Only rarely have effects of the factors been studied in combination[@Young2020].
Moreover, the usual paradigms used in ER choice research (e.g., Sheppes et al.[@Sheppes2011]) can only estimate how a factor tends to drive the choice in one direction or the other.
However, it cannot be determined in this way what internal subjective value individuals attribute to the choice options.
We are confident that we have succeeded in this with the present paradigm.
On the one hand, we were able to show which factors influence the values, but on the other hand, we were able to show the actual practical relevance of the values.
The highest SVs of the individuals were associated with the choice made by the participants. 
Until now, it has been difficult to transfer such findings from the laboratory to everyday life[@Wilms2020].
This may be due to the fact that in laboratory studies, the choice options are often predetermined by the design of the experiment [@Sheppes2011;@Sheppes2014;@Scheffel2021].
It was therefore attempted to investigate ER choice and influencing factors in everyday life.
However, even there, certain strategies were often prescribed (for example studies, see English et al.[@English2017], Millgram et al.[@Millgram2019], Wilms et al.[@Wilms2020]). 
Although these covered a large area of the emotion-genesis process[@Gross1998emerging], they were nevertheless ultimately fixed.
Of course, the calculation of SVs in our new CAD paradigm is tied to the strategies with which the strategy of interest is compared.
However, it would be possible to use ecological momentary assessment to capture ER strategies[@Koval2020].
This would allow all strategies of the ER repertoire to be recorded for each individual[@Aldao2015]. 
Also those that are rarely used or even marked as maladaptive, such as alcohol consumption or rumination[@Pena-Sarrionandia2015].
